---
title: "Configuring Google Sheets and GitHub for Kyber"
description: >
  Learn how to configure Google Sheets and GitHub for Kyber.
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Configuring Google Sheets and GitHub for Kyber}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

The main purpose of Kyber is to automate common tasks that need to be done
before the start of an Openscapes Champions Cohort. This level of automation 
requires that you authorize your computer with Google Sheets and with GitHub.

# Configuring Google Sheets

Kyber interacts with Google Sheets via the `googlesheets4` package. This
package makes it easy to authorize your computer so that Kyber can access Google
Sheets programmatically. Run the following code to configure `googlesheets4`:

```{r, eval=FALSE}
library(googlesheets4)

gs4_auth()
```

This function should redirect you to a web browser where you can log in with
your Google account. After you have authorized `googlesheets4`, you can
confirm that it is configured correctly by running the following:

```{r, eval=FALSE}
gs4_user()
#> Logged in to googlesheets4 as your-name@email.com.
```

For more detailed information, see the
[`gs4_auth()` documentation](https://googlesheets4.tidyverse.org/reference/gs4_auth.html) 
and the `googlesheets4` authorization 
[troubleshooting documentation](https://googlesheets4.tidyverse.org/articles/auth.html).

## Troubelshooting Google Sheets

If you have not authorized your computer to use `googlesheets4` in a while you
may see the following error:

```
The googlesheets4 package is requesting access to your Google account.
Select a pre-authorised account or enter '0' to obtain a new token.
Press Esc/Ctrl + C to cancel.

1: username@email.com

Selection: 1
Auto-refreshing stale OAuth token.
Error in `gargle_abort_request_failed()`:
! Client error: (403) PERMISSION_DENIED
...
```

We have had success troubleshooting this error with the following method. First,
try reading a Google Sheet into R:

```{r, eval=FALSE}
library(googlesheets4)

cohort_registry_url <- "https://docs.google.com/spreadsheets/sheet-url..."

read_sheet(cohort_registry_url)
```

You should see the following prompt:

```
Selection: 
```

Enter `0` then press the Enter key. You computer's browser should launch and
load Google's authorization page. Reauthorize your account via the web browser
and you should see the following message in the R console:

```
Waiting for authentication in browser...
Press Esc/Ctrl + C to abort
Authentication complete.
```

# Configuring GitHub

One of the main purposes of Kyber is to automate processes that people would
normally do "by hand." By authorizing Kyber with your GitHub account, you are
allowing Kyber to act "as you" on GitHub. 

🚨 A word of caution: take care in using Kyber functions that interact with GitHub. Kyber is designed so that you cannot delete things on GitHub with Kyber, 
however if you are determined you could use Kyber to make a big mess. If you
are going to write your own code or functions that use Kyber, try to avoid
using Kyber within any code that is designed to iterate or execute multiple
commands. This includes `for` and `while` loops, and mapping functions like
`sapply()` and `purrr::map()`.

To get started configuring GitHub, first make sure that you have a 
[GitHub](https://github.com/) account and that you are logged in.


The following code will 

```{r}
library(usethis)


create_github_token(
  scopes = c("repo", "user", "gist", "workflow", "admin:org"), 
  description = paste0("kyber-", Sys.Date())
)
```

```

library(gitcreds)
gitcreds_set()
```


