---
title: "Configuring Google Sheets and GitHub for Kyber"
description: >
  Learn how to configure Google Sheets and GitHub for Kyber.
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Configuring Google Sheets and GitHub for Kyber}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

The main purpose of Kyber is to automate common tasks that need to be done
before the start of an Openscapes Champions Cohort. This level of automation 
requires that you authorize your computer with Google Sheets and with GitHub.

# Configuring Google Sheets

Kyber interacts with Google Sheets via the `googlesheets4` package. This
package makes it easy to authorize your computer so that Kyber can access Google
Sheets programmatically. Run the following code to configure `googlesheets4`:

```{r, eval=FALSE}
library(googlesheets4)

gs4_auth()
```

This function should redirect you to a web browser where you can log in with
your Google account. After you have authorized `googlesheets4`, you can
confirm that it is configured correctly by running the following:

```{r, eval=FALSE}
gs4_user()
#> Logged in to googlesheets4 as your-name@email.com.
```

For more detail information, see the
[`gs4_auth()` documentation](https://googlesheets4.tidyverse.org/reference/gs4_auth.html) 
and the `googlesheets4` authorization 
[troubleshooting documentation](https://googlesheets4.tidyverse.org/articles/auth.html).

# Configuring GitHub

One of the main purposes of Kyber is to automate processes that people would
normally do "by hand." By authorizing Kyber with your GitHub account, you are
allowing Kyber to act "as you" on GitHub. The following code will 

```{r}
library(usethis)


create_github_token(
  scopes = c("repo", "user", "gist", "workflow", "admin:org"), 
  description = paste0("kyber-", Sys.Date())
)
```

```

library(gitcreds)
gitcreds_set()
```


