---
title: "Create Cohort Certificates"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Create Cohort Certificates}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup}
#| eval: false
library(kyber)
library(googlesheets4)
library(dplyr)
```

## Create a single certificate

For a single certificate, you can supply all of the values manually:

```{r}
#| eval: false

create_certificate(
  cohort_name = "2023-fred-hutch",
  first_name = "First Name",
  last_name = "Last Name",
  start_date = "2023-09-19",
  end_date = "2023-10-19",
  cohort_website = "https://openscapes.github.io/2023-fred-hutch/"
)
```

## Create a batch of certificates for a cohort

First load data from a cohort google sheet:

```{r}
#| eval: false

registry <- read_sheet("https://docs.google.com/spreadsheets/d/1Ys9KiTXXmZ_laBoCV2QWEm7AcnGSVQaXvm2xpi4XTSc") # OpenscapesChampionsCohortRegistry
participants <- read_sheet("URL to OpenscapesParticipantsMainList")
```

Then call the `create_batch_certificates()` function to create the certificates:

```{r}
#| eval: false

create_batch_certificates(
  registry = registry,
  participants = participants,
  cohort_name = "2023-fred-hutch",
  output_dir = "~/Desktop/fred-hutch-certificates"
)

```

## Create a batch of certificates for NMFS Openscapes cohorts

The process is the same as for the standard cohorts, but set the `cohort_type` 
parameter to `"nmfs"`, and it will use the appropriate NMFS Openscapes template.

```{r}
#| eval: false

create_batch_certificates(
  registry = registry,
  participants = participants,
  cohort_name = "2024-nmfs-champions-a",
  cohort_type = "nmfs",
  output_dir = "~/Desktop/2024-nmfs-champions-a"
)

```
