---
title: "Creating a Cohort-Specific GitHub Repository with Kyber"
description: >
  Learn how to create a cohort-specific GitHub repository with Kyber.
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Creating a Cohort-Specific GitHub Repository with Kyber}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Configure GitHub

Make sure your computer is configured according to the instructions in
`vignette("configuration")`. Run the following code to see if your GitHub
credentials are set up:

```{r, eval=FALSE}
library(gitcreds)
gitcreds_get()
```

If credentials are detected you should get a result like:

```
<gitcreds>
  protocol: https
  host    : github.com
  username: PersonalAccessToken
  password: <-- hidden -->
```

# Creating the Repository

Each Champions Cohort has its own GitHub repository. The name of the repository
should match the corresponding `cohort_name` in the [Cohort Registry](cr). The
`init_repo()` function in the code below will do the following:

1. It checks to see if the GitHub repository you are trying to create already
exists. If it does exist, it will result in an error.
2. It tries to initialize a GitHub repository on your computer. If that 
repository already exists in the `path` argument, it will result in an error.
No repository will have been created on GitHub.
3. It will then create the local Git repository, add a code of conduct (via
`add_code_of_conduct()`), add a `.gitignore` file (via `add_gitignore()`), and
then `git add` and `git commit` those files before `git push`-ing those files
to GitHub.
4. Finally it will create a `README.Rmd` file in the repository for you to edit.

```{r, eval=FALSE}
library(kyber) 

repo_name <- "2021-ilm-rotj"

repo_path <- init_repo(repo_name)
```



[cr]: https://docs.google.com/spreadsheets/d/1Ys9KiTXXmZ_laBoCV2QWEm7AcnGSVQaXvm2xpi4XTSc/edit#gid=695033382