
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

## libraries
library(tidyverse)

## TODO read in Google Doc registry sheet
cohort_info <- tibble(cohort_name = "2022-faseb",
                      date_start = "01/28/2021",
                      time_start = "10:00am PT", 
                      cohort_type = "core-4calls",
                      website = "https://openscapes.github.io/2022-faseb",
                      google_drive_folder = "TODO"
)


## TODO depending on cohort_type, read in Google Doc sheet
call_info <- tibble(call = 1, 
                    title = "Openscapes Mindset",
                    topic1 = "Openscapes Mindset",
                    topic2 = "Onboarding", 
                    goals = "We'll start working towards a common understanding...",
                    roll-call = "Share something you're good at"
)
  
```

# Call 1: `r call_info$title`

Openscapes Champions Cohort Series [ `r cohort_info$cohort_name` ] 

`r date_start`. `r time_start`. 

Links: [Cohort Google Drive folder]( `r cohort_info$google_drive_folder` ), Zoom: 
  
Web: `r cohort_info$website`
  
  **Quick introduction: **
  
  * Welcome, thank you for being here! 
  * We’ll be using Zoom for video calls & Google docs for notes 
* Everything you share in this doc is available to everyone else on the call
* Comments / emojis / gifs / +1s to say “me too” are welcome! 🎉🤓
* As you join each session, please:
  * Add your name to the Roll Call below
* Rename yourself as how you’d like to be called and add your team name
* Hover over your name or video > 3 dots > rename


---
  
  
## Agenda
  
**Today:**  `r call_info$goals`


## Roll call • `r cohort_info$time_start` - `r cohort_info$time_start + 2`

_Name / pronouns / [team]() / `r call_info$roll-call`

* 
*    
*   
*  
* 
*  
*  
*  
* 
*  

## Welcome • 10:02-10:15 PT

```{r, child = either "welcome-first.md" or "welcome-core.md"}

```


```{r, child = "welcome-overview.md"}

```

## Introductions OR Reflections • 10:15-10:30 PT

```{r, child = "introductions.md"}

```


## `r call_info$topic1` • 10:30-11:10 PT

_All Champions program slides are also linked from [https://openscapes.org/series](https://openscapes.github.io/series) _

```{r, child = "introductions.md"}
# note: slide link is in this .md right now, so can easily re-use in digests
```

## `r call_info$topic2` • 10:10-11:25 PT

```{r, child = "onboarding.md"}
# note: slide link is in this .md right now, so can easily re-use in digests
```

## Closing • 11:25-11:30 PT

```{r}
## note to Sean -- not sure the following should be markdown templates or be shorter parameters from the cohort registry: https://docs.google.com/spreadsheets/d/1Oej46BMX_SLIc1cwoyLHzNWwGlT3szez8FDKc3b418w/edit#gid=942365997
```



* **Task for next time: Have a Seaside Chat & start your Pathway** (3 min) – All 
    * 1) Have a Seaside Chat with your research group to explore/practice GitHub. Options:
        * a) Join a GitHub Clinic with us (Google Calendar Invites upcoming)
            * Sept 13, 12-1pm PT 
            * Sept 14, 9-10am PT
        * b) Follow along on your own ([slides](https://docs.google.com/presentation/d/1PzGAbEpNhT6CDPe1DCHf5-eVAjy-2R2D3VMHz7dY774/edit#slide=id.p) & recording)
        * *share your GitHub username ahead of time: [OpenscapesParticipants](https://docs.google.com/spreadsheets/d/1BKxaZgv7iVkG2n8lGZVGIJcv8iObdEty9tgbov2fuH4/edit#gid=0)
    * 2) Start thinking about your Pathway: Focus on your trailhead (now). 
        * [Pathways Sheet](https://drive.google.com/open?id=1X_-qPdWDCpw2F3nZr6vZnq87guyUIGLvekm0XV2H-A8) (File > Make a copy)
        * Upload to THIS PathwayShare FOLDER folder before Call 4
    * 3) Join Slack (we’ll invite you to our Openscapes org)
        * Introduce yourself and tag your team
            * Private channel for our cohort as you get comfortable 
            * New to Slack? [quickstart doc](https://zenodo.org/record/3763730#.YIxK6-tlDUI)
* **Connecting between sessions**
    * https://openscapes.github.io/2021-sasi - details & links
    * Slack
    * Twitter – [@openscapes](https://twitter.com/openscapes) 
    * Call Digest next week 
* **Efficiency Tip of the Day **(3 min) – Julie
* Keyboard Shortcuts Part 1: Useful for any application (docs, email, code)
    * **Mac: **Arrow keys + option, + command, + shift, & in combination
    * **PC:** Arrow keys + Ctrl + Fn + shift, & in combination
    * Here is some sample text for our demo. What a great sentence.
* **Inclusion Tip of the Day**
    * Be mindful of words and idioms you use. Move away from language that is racist, sexist, violent, ableist, etc. Example: 
        * Use “main” instead of “master” (GitHub branches, bedrooms)
        * Welcome people to meetings with gender-neutral/gender-inclusive language, like “Hi all/everyone/folks/team” instead of “Hi guys/ladies”
        * Others?
        *  
* **Announcements **(please contribute!)
    * **Sept 30, 12pm PT: Openscapes Community Call: RMarkdown chat with Alison Hill of RStudio: **[https://openscapes.github.io/events/](https://openscapes.github.io/events/) 
    * **Sept 21, 7pm PT: [Relations First, with Ta7talíya Nahanee](https://www.eventbrite.ca/e/relations-first-with-ta7taliya-nahanee-tickets-167114803877)**
    *  
    *  
    *  
* **Requests for peer-assists **(please share what you need and how you can assist!)
    *  
    *  
    * 
* **<span style="text-decoration:underline;">Resources</span>** available for reuse/remix
    * [openscapes.org](https://openscapes.org)
        * [/series](https://openscapes.github.io/series): Champions program lesson series
        * [/media](https://openscapes.org/media): slide decks, publications, media
        * [/blog](https://openscapes.org/blog): stories from the community
    * github: [@openscapes](https://github.com/openscapes)
        * [how_we_work](https://github.com/Openscapes/how_we_work), [seaside-chats](https://github.com/Openscapes/seaside-chats): Examples from previous cohorts
    * twitter: [@openscapes](https://twitter.com/openscapes)
    * artwork: by the incredible [Allison Horst](https://twitter.com/allison_horst)
* **Feedback on this session**
    * What worked? What didn’t? What surprised you? What would you change? 
        *  
        *  
        *  

 

Thank you, see you next time!
